# Generate records with sequence IDs (cached in .csv below)
```{r}
source(here("src", "functions.r"))
```

```{r}
df_out_visits <- df_outpatient_visits_preprocessed %>%
  mutate(patient_clinic_id = paste0(dw_ek_borger, dw_sk_lpr3forloebsansvar, dw_sk_kontakt))
```


```{r}
df_out_visits_relabel_as_most_severe <- df_out_visits %>%
  relabel_diag_most_severe(patient_clinic_id)
```

```{r}
df_out_visits_relabel_as_last_diag <- df_out_visits %>%
  recode_diagnoses_with_last_in_sequence(patient_clinic_id)
```

```{r}
df_out_courses <- df_out_visits %>%
  visits_to_processed_treatment_courses()
```

# Open sequences in each period 
```{r}
df_n_open_courses_by_period <- df_out_courses %>%
  count_open_sequences_in_period()
```

# Truncation df
```{r}
df_truncation <- list()

df_truncation$fx <- df_outpatient_visits_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars = 2)

df_truncation$fxx <- df_outpatient_visits_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars = 3)

df_truncation$fxxx <- df_outpatient_visits_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars = 4)

df_truncation$fxxxx <- df_outpatient_visits_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars = 5)
```

```{r}
df_truncation$estimates <- df_truncation$fx %>%
  right_join(df_truncation$fxx) %>%
  right_join(df_truncation$fxxx) %>%
  right_join(df_truncation$fxxxx) %>%
  right_join(df_n_open_courses_by_period) %>%
  filter(period > "2013-01-01", period < "2021-04-02") %>%
  pivot_longer(cols = 2:5, names_to = "truncation_level", values_to = "count") %>%
  add_poisson_test_column(count_col = count, opportunities_col = open_sequences) %>%
  mutate(truncation_level = case_when(
    truncation_level == "unique_diagnoses_2" ~ "FX",
    truncation_level == "unique_diagnoses_3" ~ "FXX",
    truncation_level == "unique_diagnoses_4" ~ "FXX.X",
    truncation_level == "unique_diagnoses_5" ~ "FXX.XX"
  ))
```



# Default
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_n_patient_diagnoses_by_quarter <- df_outpatient_visits_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars = 3) # Number_of_chars = 3 is equal to using F34
```

## Join and calculate diagnoses per open sequence
```{r}
df_n_diag_per_patient <- join_and_calculate_diagnoses_per_open_sequence(
  df_n_open_courses_by_period,
  df_n_patient_diagnoses_by_quarter
)
```

# Most severe
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_n_patient_diagnoses_by_quarter_most_severe <- df_out_visits_relabel_as_most_severe %>%
  count_unique_diagnoses_in_period()
```

## Join and calculate diagnoses per patient
```{r}
df_n_diag_per_patient_most_severe <- join_and_calculate_diagnoses_per_open_sequence(
  df_n_open_courses_by_period,
  df_n_patient_diagnoses_by_quarter_most_severe
)
```


# Final diagnosis
## Unique diagnoses in each period 
```{r}
df_n_patient_diagnoses_by_quarter_final_visit <- df_out_visits_relabel_as_last_diag %>%
  count_unique_diagnoses_in_period()

```

## Join and calculate diagnoses per patient
```{r}
df_n_diag_per_patient_final_visit <- join_and_calculate_diagnoses_per_open_sequence(
  df_n_open_courses_by_period,
  df_n_patient_diagnoses_by_quarter_final_visit
)
```


# Plot
## By mitigation
### Data-wrangling
#### Combine DFs
```{r fig.height=5, fig.width=10}
source(here("src", "individual_unique_diagnoses_functions.r"))
source(here("src", "functions.r"))

df_plot_mitigation_seq_responsibility_id <- create_mitigation_df(
  df_default = df_n_diag_per_patient,
  df_most_severe = df_n_diag_per_patient_most_severe,
  df_last_visit_only = df_n_diag_per_patient_final_visit
) %>% ungroup()

df_plot_mitigation_seq_responsibility_id <- write_csv(df_plot_mitigation_seq_responsibility_id, here("csv", "df_plot_mitigation_seq_responsibility_id"))
```


#### Add p-values
```{r}
df_plot_mitigation_seq_responsibility_id <- read_csv(here("csv", "df_plot_mitigation_seq_responsibility_id"))

##### What to report?
##### pdq(0,0,0) = linear model / z.test (no detrending)
##### pdq(0,1,0) = liear model with differencing
##### pdq(1,1,0) = autoregressive model with differencing

p_load(
  fable,
  tsibble,
  feasts,
  urca
)

df_plot_mitigation_seq_responsibility_id_p_values <- df_plot_mitigation_seq_responsibility_id %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1)) %>%
  mutate(period = yearquarter(period)) %>%
  select(diag_per_active, period, origin, lpr3) %>%
  as_tsibble(key = origin, index = period) %>%
  model(arima = ARIMA(diag_per_active ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  ungroup() %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = 70), # 3 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  ) %>%
  filter(period == max(period)) %>%
  select(period, diag_per_active, origin) %>%
  left_join(df_plot_mitigation_seq_responsibility_id_p_values, by = "origin")
```

### Generate plot
```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

mitigation_seq_responsibility_id_incident_plot <- save_incident_per_active_plot(
  df = df_plot_mitigation_seq_responsibility_id,
  filename = "mitigation_seq_responsibility_id_incident",
  exclusive_column_for_lpr2 = "Unmitigated",
  p_values = df_plot_mitigation_seq_responsibility_id_p_values_2,
  nudge_constant = 0.001
)

mitigation_seq_responsibility_id_incident_plot
```


## By truncation 
```{r}
## What to report?
## pdq(0,0,0) = linear model / z.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing

## binary indicator for date in LPR2/LPR3
df_truncation$p_values <- df_truncation$estimates %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1)) %>%
  mutate(period = yearquarter(period)) %>%
  as_tsibble(key = truncation_level, index = period) %>%
  model(arima = ARIMA(estimate ~ 1 + lpr3 + pdq(1, 1, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = 70), # 4 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  )


df_truncation$p_values <- df_truncation$p_values %>%
  mutate(period = max(df_truncation$estimates$period))
```

```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

truncation_plot <- save_truncation_plot(
  df = df_truncation$estimates,
  filename = "examine_truncation_individual_unique_diagnoses_by_quarter_p_values",
  p_values = df_truncation$p_values
)

truncation_plot
```

### Combined
```{r}
combined <- save_combined_plots(
  truncation_plot,
  mitigation_seq_responsibility_id_incident_plot,
  "figure_4"
)

combined
```


# Table
```{r}
df_n_patient_diagnoses_by_quarter

df_n_patient_diagnoses_by_quarter_final_visit

df_n_patient_diagnoses_by_quarter_most_severe

df_table <- df_n_open_courses_by_period %>%
  right_join(df_n_patient_diagnoses_by_quarter) %>%
  rename(unique_diagnoses_default = unique_diagnoses_fxx) %>%
  right_join(df_n_patient_diagnoses_by_quarter_most_severe) %>%
  rename(unique_diagnoses_most_severe = unique_diagnoses_fxx) %>%
  right_join(df_n_patient_diagnoses_by_quarter_final_visit) %>%
  rename(unique_diagnoses_final_visit = unique_diagnoses_fxx)
```