# Generate records with sequence IDs (cached in .csv below)
## No threshold
```{r}
df_outpatient_constructed_no_threshold <- df_outpatient_preprocessed %>%
  add_patient_and_clinic_uid(
    clinic_id_col = shakafskode_besoeg,
    patient_id_col = dw_ek_borger
  )
```

```{r}
df_outpatient_constructed_no_threshold_most_severe <- df_outpatient_constructed_no_threshold %>% 
  relabel_diag_most_severe(constructed_id)
  
```

```{r}
df_outpatient_constructed_no_threshold_last_visit <- df_outpatient_constructed_no_threshold %>% 
  recode_diagnoses_with_last_in_sequence(constructed_id)
```

# Open sequences in each period 
```{r}
source(here("src", "functions.r"))

df_sequenced_default <- df_outpatient_constructed_no_threshold %>%
  convert_to_sequences_for_incident_per_active()
```

```{r}
df_open_sequences_in_period <- df_sequenced_default %>% 
  count_open_sequences_in_period()
```

# Truncation df
```{r}
df_truncation <- list()

df_truncation$fx <- df_outpatient_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars=2)

df_truncation$fxx <- df_outpatient_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars=3)

df_truncation$fxxx <- df_outpatient_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars=4)

df_truncation$fxxxx <- df_outpatient_preprocessed %>%
  count_unique_diagnoses_in_period(number_of_chars=5)
```

```{r}
df_truncation$estimates <- df_truncation$fx %>% 
  right_join(df_truncation$fxx) %>% 
  right_join(df_truncation$fxxx) %>% 
  right_join(df_truncation$fxxxx) %>% 
  right_join(df_open_sequences_in_period) %>% 
  filter(period > "2013-01-01", period < "2021-04-02") %>% 
  pivot_longer(cols = 2:5, names_to = "truncation_level", values_to = "count") %>% 
  add_poisson_test_column(count_col = count, opportunities_col = open_sequences) %>% 
  mutate(truncation_level = case_when(
    truncation_level == "unique_diagnoses_2" ~ "FX",
    truncation_level == "unique_diagnoses_3" ~ "FXX",
    truncation_level == "unique_diagnoses_4" ~ "FXX.X",
    truncation_level == "unique_diagnoses_5" ~ "FXX.XX"
  ))
```



# Default
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_unique_in_period <- df_outpatient_preprocessed %>% 
  count_unique_diagnoses_in_period(number_of_chars=3) # Number_of_chars = 3 is equal to using F34
```

## Join and calculate diagnoses per open sequence
```{r}
df_per_patient <- join_and_calculate_diagnoses_per_open_sequence(
  df_open_sequences_in_period,
  df_unique_in_period
)
```

# Most severe
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_unique_in_period_no_threshold_most_severe <- df_outpatient_constructed_no_threshold_most_severe %>% 
  count_unique_diagnoses_in_period()
```

## Join and calculate diagnoses per patient
```{r}
df_per_patient_most_severe <- join_and_calculate_diagnoses_per_open_sequence(
  df_open_sequences_in_period,
  df_unique_in_period_no_threshold_most_severe
)
```





# Final diagnosis
```{r}
df_outpatient_constructed_no_threshold_final_visit <- read_csv(here("csv", "df_outpatient_constructed_no_threshold_final_visit.csv"))

```

## Convert to sequences
```{r}
source(here("src", "functions.r"))

df_sequenced_final_visit <- df_outpatient_constructed_no_threshold_final_visit %>%
  convert_to_sequences_for_incident_per_active()
```

## Unique diagnoses in each period 
```{r}
df_unique_in_period_no_threshold_final_visit <- df_outpatient_constructed_no_threshold_final_visit %>% 
  count_unique_diagnoses_in_period()
  
```

## Join and calculate diagnoses per patient
```{r}
df_per_patient_final_visit <- join_and_calculate_diagnoses_per_open_sequence(
  df_open_sequences_in_period,
  df_unique_in_period_no_threshold_final_visit
)
```





# Plot
## By mitigation
### Data-wrangling
#### Combine DFs
```{r fig.height=5, fig.width=10}
source(here("src", "individual_unique_diagnoses_functions.r"))
source(here("src", "functions.r"))

df_mitigation_constructed_incident_no_threshold_plot <- create_mitigation_df(
  df_default = df_per_patient,
  df_most_severe = df_per_patient_most_severe,
  df_last_visit_only = df_per_patient_final_visit
)

write_csv(df_mitigation_constructed_incident_no_threshold_plot, here("csv", "df_mitigation_constructed_incident_no_threshold_plot.csv"))
```

```{r}
df_mitigation_constructed_incident_no_threshold_plot <- read_csv(here("csv", "df_mitigation_constructed_incident_no_threshold_plot.csv"))
```

#### Add p-values
```{r}
##### What to report?
##### pdq(0,0,0) = linear model / z.test (no detrending)
##### pdq(0,1,0) = liear model with differencing
##### pdq(1,1,0) = autoregressive model with differencing

p_load(
  fable, 
  tsibble, 
  feasts, 
  urca
)

df_mitigation_constructed_incident_no_threshold_plot_p_values <- df_mitigation_constructed_incident_no_threshold_plot %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1)) %>%
  mutate(period = yearquarter(period)) %>% 
  select(diag_per_active, period, origin, lpr3) %>%
  as_tsibble(key = origin, index = period) %>%
  model(arima = ARIMA(diag_per_active ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  ungroup() %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = 70), # 3 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  )

df_mitigation_constructed_incident_no_threshold_plot_p_values_2 <- df_mitigation_constructed_incident_no_threshold_plot %>%
   filter(period == max(period)) %>%
   select(period, diag_per_active, origin) %>%
   left_join(df_mitigation_constructed_incident_no_threshold_plot_p_values, by = "origin")
```

### Calculate SDs
```{r}
df_sds <- df_mitigation_constructed_incident_no_threshold_plot %>% 
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1))

df_before <- df_sds %>% 
  filter(lpr3 == 0) %>% 
  filter(origin == "Unmitigated")

df_after <- df_sds %>% 
  filter(lpr3 == 1) %>% 
  filter(origin == "Unmitigated")

sd(df_before$diag_per_active)
sd(df_after$diag_per_active)
```


### Generate plot
```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

mitigation_constructed_incident_no_threshold_plot <- save_incident_per_active_plot(
  df = df_mitigation_constructed_incident_no_threshold_plot,
  filename = "mitigation_constructed_incident_no_threshold",
  exclusive_column_for_lpr2 = "Unmitigated",
  p_values = df_mitigation_constructed_incident_no_threshold_plot_p_values_2,
  nudge_constant = 0.001
)

mitigation_constructed_incident_no_threshold_plot
```


## By truncation 
```{r}
## What to report?
## pdq(0,0,0) = linear model / z.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing

## binary indicator for date in LPR2/LPR3
df_truncation$p_values <- df_truncation$estimates %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1)) %>%
  mutate(period = yearquarter(period)) %>%
  as_tsibble(key = truncation_level, index = period) %>%
  model(arima = ARIMA(estimate ~ 1 + lpr3 + pdq(1, 1, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = 70), # 4 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  ) 


df_truncation$p_values <- df_truncation$p_values %>% 
  mutate(period = max(df_truncation$estimates$period))
```

```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

truncation_plot <- save_truncation_plot(
  df = df_truncation$estimates,
  filename ="examine_truncation_individual_unique_diagnoses_by_quarter_p_values",
  p_values = df_truncation$p_values
)

truncation_plot
```

### Combined
```{r}
combined <- save_combined_plots(truncation_plot,
                                mitigation_constructed_incident_no_threshold_plot,
                                "figure_s4")

combined
```



# Table
```{r}
df_unique_in_period 

df_unique_in_period_no_threshold_final_visit

df_unique_in_period_no_threshold_most_severe

df_table <- df_open_sequences_in_period %>% 
  right_join(df_unique_in_period) %>% 
  rename(unique_diagnoses_default = unique_diagnoses_3) %>% 
  right_join(df_unique_in_period_no_threshold_most_severe) %>% 
  rename(unique_diagnoses_most_severe = unique_diagnoses_3) %>% 
  right_join(df_unique_in_period_no_threshold_final_visit) %>% 
  rename(unique_diagnoses_final_visit = unique_diagnoses_3) %>% 
  mutate(ratio = unique_diagnoses_default/open_sequences)
```