Identical to out_seq_responsibility_id, but where mitigation strategies consider visits to be part of the same treatment course if they're by the same patient to the same clinic.

# Generate records with sequence IDs (cached in .csv below)
## No threshold
```{r}
df_out_visits <- df_outpatient_visits_preprocessed %>%
  add_patient_clinic_uid(clinic_id_col=shakafskode_besoeg, patient_id_col=dw_ek_borger)
```

```{r}
df_out_visits_relabel_as_most_severe <- df_out_visits %>%
  relabel_diag_most_severe(patient_clinic_uid)
```

```{r}
df_out_visits_relabel_as_last_diag <- df_out_visits %>%
  relabel_diag_with_last_in_sequence(patient_clinic_uid)
```

# Open sequences in each period 
```{r}
source(here("src", "functions.r"))

df_out_courses <- df_out_visits %>%
  visits_to_processed_treatment_courses()
```

```{r}
df_open_sequences_in_period <- df_out_courses %>%
  count_open_sequences_in_period()
```

# Truncation df
```{r}
df_truncation <- list()

df_truncation$fx <- df_outpatient_visits_preprocessed %>%
  count_uniq_diags_per_pt_in_period(n_chars = 2)

df_truncation$fxx <- df_outpatient_visits_preprocessed %>%
  count_uniq_diags_per_pt_in_period(n_chars = 3)

df_truncation$fxxx <- df_outpatient_visits_preprocessed %>%
  count_uniq_diags_per_pt_in_period(n_chars = 4)

df_truncation$fxxxx <- df_outpatient_visits_preprocessed %>%
  count_uniq_diags_per_pt_in_period(n_chars = 5)
```

```{r}
df_truncation$estimates <- df_truncation$fx %>%
  right_join(df_truncation$fxx) %>%
  right_join(df_truncation$fxxx) %>%
  right_join(df_truncation$fxxxx) %>%
  right_join(df_open_sequences_in_period) %>%
  filter(period > start_date_str, period < end_date_str) %>%
  pivot_longer(cols = 2:5, names_to = "truncation_level", values_to = "count") %>%
  add_poisson_columns(count_col = count, opportunities_col = open_sequences) %>%
  mutate(truncation_level = case_when(
    truncation_level == "unique_diagnoses_2" ~ "FX",
    truncation_level == "unique_diagnoses_3" ~ "FXX",
    truncation_level == "unique_diagnoses_4" ~ "FXX.X",
    truncation_level == "unique_diagnoses_5" ~ "FXX.XX"
  ))
```



# Default
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_n_patient_diagnoses_by_quarter <- df_outpatient_visits_preprocessed %>%
  count_uniq_diags_per_pt_in_period(n_chars = 3) # Number_of_chars = 3 is equal to using F34
```

## Join and calculate diagnoses per open sequence
```{r}
df_n_diag_per_patient <- calc_diag_per_treatment_course(
  df_open_sequences_in_period,
  df_n_patient_diagnoses_by_quarter
)
```

# Most severe
## Convert to sequences
```{r}
source(here("src", "functions.r"))
```

## Unique diagnoses in each period 
```{r}
df_n_patient_diagnoses_by_quarter_most_severe <- df_out_visits_relabel_as_most_severe %>%
  count_uniq_diags_per_pt_in_period()
```

## Join and calculate diagnoses per patient
```{r}
df_n_diag_per_patient_most_severe <- calc_diag_per_treatment_course(
  df_open_sequences_in_period,
  df_n_patient_diagnoses_by_quarter_most_severe
)
```

# Final diagnosis
## Convert to sequences
```{r}
df_n_patient_diagnoses_by_quarter_final_visit <- df_out_visits_relabel_as_last_diag %>%
  count_uniq_diags_per_pt_in_period()
```

## Join and calculate diagnoses per patient
```{r}
df_n_diag_per_patient_final_visit <- calc_diag_per_treatment_course(
  df_open_sequences_in_period,
  df_n_patient_diagnoses_by_quarter_final_visit
)
```

# Plot
## By mitigation
### Data-wrangling
#### Combine DFs
```{r fig.height=5, fig.width=10}
source(here("src", "individual_unique_diagnoses_functions.r"))
source(here("src", "functions.r"))

df_plot_mitigation_same_clinic <- create_mitigation_df(
  df_default = df_n_diag_per_patient,
  df_most_severe = df_n_diag_per_patient_most_severe,
  df_last_visit_only = df_n_diag_per_patient_final_visit
)

write_csv(df_plot_mitigation_same_clinic, here("csv", "df_plot_mitigation_same_clinic.csv"))
```

```{r}
df_plot_mitigation_same_clinic <- read_csv(here("csv", "df_plot_mitigation_same_clinic.csv"))
```

#### Add p-values
```{r}
##### What to report?
##### pdq(0,0,0) = linear model / z.test (no detrending)
##### pdq(0,1,0) = liear model with differencing
##### pdq(1,1,0) = autoregressive model with differencing

p_load(
  fable,
  tsibble,
  feasts,
  urca
)

df_plot_mitigation_same_clinic_p_values <- df_plot_mitigation_same_clinic %>%
  mutate(lpr3 = if_else(period < transition_date_str, 0, 1)) %>%
  mutate(period = yearquarter(period)) %>%
  select(estimate, period, origin, lpr3) %>%
  as_tsibble(key = origin, index = period) %>%
  model(tslm = TSLM(estimate ~ 1 + lpr3)) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  ungroup() %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = n_stat_tests), # 3 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  ) 

df_p_values_by_period <- df_plot_mitigation_same_clinic %>%
  filter(period == max(period)) %>%
  select(period, estimate, origin) %>%
  left_join(df_plot_mitigation_same_clinic_p_values, by = "origin")
```

### Calculate SDs
```{r}
df_sds <- df_plot_mitigation_same_clinic %>%
  mutate(lpr3 = if_else(period < transition_date_str, 0, 1))

df_before <- df_sds %>%
  filter(lpr3 == 0) %>%
  filter(origin == "Unmitigated")

df_after <- df_sds %>%
  filter(lpr3 == 1) %>%
  filter(origin == "Unmitigated")

sd(df_before$estimate)
sd(df_after$estimate)
```


### Generate plot
```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

mitigation_constructed_incident_no_threshold_plot <- save_incident_per_active_plot(
  df = df_plot_mitigation_same_clinic,
  filename = "mitigation_constructed_incident_no_threshold",
  exclusive_column_for_lpr2 = "Unmitigated",
  p_values = df_p_values_by_period,
  nudge_constant = 0.001
)

mitigation_constructed_incident_no_threshold_plot
```


## By truncation 
```{r}
## binary indicator for date in LPR2/LPR3
df_truncation$p_values <- df_truncation$estimates %>%
  mutate(lpr3 = if_else(period < transition_date_str, 0, 1)) %>%
  mutate(period = yearquarter(period)) %>%
  as_tsibble(key = truncation_level, index = period) %>%
  model(tslm = TSLM(estimate ~ 1 + lpr3)) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr", n = n_stat_tests), # 4 comparisons
    significant = if_else(corrected_p < 0.05, "*", "")
  )


df_truncation$p_values <- df_truncation$p_values %>%
  mutate(period = max(df_truncation$estimates$period))
```

```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

truncation_plot <- save_truncation_plot(
  df = df_truncation$estimates,
  filename = "examine_truncation_individual_unique_diagnoses_by_quarter_p_values",
  p_values = df_truncation$p_values
)

truncation_plot
```

### Combined
```{r}
combined <- save_combined_plots(
  truncation_plot,
  mitigation_constructed_incident_no_threshold_plot,
  "figure_s4"
)

combined
```



# Table
```{r}
df_n_patient_diagnoses_by_quarter

df_n_patient_diagnoses_by_quarter_most_severe

df_n_patient_diagnoses_by_quarter_final_visit

df_table <- df_open_sequences_in_period %>%
  right_join(df_n_patient_diagnoses_by_quarter) %>%
  rename(unique_diagnoses_default = unique_diagnoses_3) %>%
  right_join(df_n_patient_diagnoses_by_quarter_most_severe) %>%
  rename(unique_diagnoses_most_severe = unique_diagnoses_3) %>%
  right_join(df_n_patient_diagnoses_by_quarter_final_visit) %>%
  rename(unique_diagnoses_final_visit = unique_diagnoses_3) %>%
  mutate(ratio = unique_diagnoses_default / open_sequences)
```