---
title: "debug_construct_sequences"
output: html_document
editor_options: 
  chunk_output_type: inline
---

## Do we lose visits when using thresholds?

```{r}
df_threshold_summarised <- df_outpatient_constructed_3m_threshold_last_visit_only
df_naive_summarised <- df_outpatient_constructed_no_threshold_last_visit_only

df_source_threshold <- df_outpatient_constructed_3m_threshold
df_source_naive <- df_outpatient_constructed_no_threshold
```


Are there an identical number of patients in periods?
```{r}
identical(
  df_threshold_summarised$n,
  df_naive_summarised$n
)
```

Is the NA rate the same?
```{r}
pacman::p_load(skimr)

skim(df_source_threshold)
skim(df_source_naive)
```

Are the source-DF dimensions the same?
```{r}
dim(df_source_threshold)
dim(df_source_naive)
```

What does "NA introduced by coercion" mean when running `recode_with_most_severe_diagnosis_for_sequence`?

```{r}
source(here("src", "functions.r"))

## undebug(recode_with_most_severe_diagnosis_for_sequence)

df_threshold_most_severe <- df_source_threshold %>%
  slice_sample(prop = 0.01) %>%
  mutate(adiagnosekode_2 = substr(adiagnosekode, 2, 2)) %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id)

df_threshold_most_severe %>%
  filter(adiagnosekode_2 == "e")
```

For some reason, about 10% of the rows don't have psychiatric diagnosis codes. This should be fixed now, since I added "keep_only_psych_visits" to preprocessing