# About

<!--chapter:end:index.rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r}
source(here("rmd", "subchapter_props", "0_setup_env.r"))
```

# Suchapter props, outpatient, naive useage of kontakt and forløbsansvar

Reduce complexity
```{r}
df_outpatient_for_subchapter <- df_raw_outpatient %>%
  filter(ambbesoeg == 1) %>%
  add_LPR23_quarter_column() %>%
  select(
    dw_ek_borger,
    datotid_start,
    dw_sk_lpr3forloebsansvar,
    dw_sk_kontakt,
    adiagnosekode,
    ambbesoeg,
    period,
    shakgeografiafskode_besoeg
  ) %>%
  rename(clinic = shakgeografiafskode_besoeg) %>%
  keep_only_psych_visits() %>%
  truncate_diagnosis_to_letter_and_digit()
```

### Naive
```{r}
df_unique_in_period_outpatient <- df_outpatient_for_subchapter %>%
  add_column_unique_pt_in_period()
```

```{r}
df_unique_with_diagnosis_outpatient <- df_outpatient_for_subchapter %>%
  add_column_n_with_diagnosis_in_period()

df_prop_diag_outpatient <- calc_prop_of_unique_patients_with_diagnosis(df_unique_in_period_outpatient, df_unique_with_diagnosis_outpatient)

log_time()
```

### Most severe
Recode with most severe from sequence
```{r}
source(here("src", "functions.r"))
df_unique_with_diagnosis_as_most_severe_outpatient <- df_outpatient_for_subchapter %>%
  recode_with_most_severe_diagnosis_for_sequence(dw_sk_kontakt, dw_sk_lpr3forloebsansvar, two_columns = TRUE) %>%
  add_column_n_with_diagnosis_in_period()
```

```{r}
source(here("src", "functions.r"))
df_prop_diag_most_severe_outpatient <- calc_prop_of_unique_patients_with_diagnosis(
  df_unique_in_period_outpatient,
  df_unique_with_diagnosis_as_most_severe_outpatient
)

log_time()
```


### Final visit
```{r}
source(here("src", "functions.r"))
df_outpatient_for_subchapter_final_visit_only <- df_outpatient_for_subchapter %>%
  recode_diagnoses_with_last_in_sequence(dw_sk_kontakt, dw_sk_lpr3forloebsansvar, two_columns = TRUE)

df_unique_with_diagnosis_outpatient_final_visit_only <- df_outpatient_for_subchapter_final_visit_only %>%
  add_column_n_with_diagnosis_in_period()

df_prop_diag_outpatient_final_visit_only <- calc_prop_of_unique_patients_with_diagnosis(
  df_unique_in_period_outpatient,
  df_unique_with_diagnosis_outpatient_final_visit_only
)

log_time()
```

## Plotting
### Forloebsansvar and LPR2 kontakt
```{r}

### Join with the receiver dataframe
df_mitigation_naive <- mutate(df_prop_diag_outpatient, origin = "Unchanged") %>%
  bind_rows(mutate(df_prop_diag_most_severe_outpatient, origin = "Most severe")) %>%
  bind_rows(mutate(df_prop_diag_outpatient_final_visit_only, origin = "Final visit"))

df_mitigation_naive_without_first_quarters <- df_mitigation_naive %>%
  filter(period > "2013-01-01")

log_time()
```

```{r}
### Plot
print(getwd())

source(here("src", "functions.r"))
source(here("src", "subchapter_props_functions.r"))

graph_subchapter_props(df_mitigation_naive,
  filename = "examine_mitigation_full_same_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

graph_subchapter_props(df_mitigation_naive,
  filename = "examine_mitigation_full_free_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

log_time()
```

```{r}
### Plot
source(here("src", "subchapter_props_functions.r"))

graph_subchapter_props(df_mitigation_naive_without_first_quarters,
  filename = "examine_mitigation_without_first_quarters_same_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

graph_subchapter_props(df_mitigation_naive_without_first_quarters,
  filename = "examine_mitigation_without_first_quarters_free_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

log_time()
```

### Testing
```{r}
pacman::p_load(fable, tsibble, feasts, urca)


df_mitigation_naive_without_first_quarters_p_values <- df_mitigation_naive_without_first_quarters %>%
  mutate(
    lpr3 = if_else(period < "2019-02-03", 0, 1),
    period = yearquarter(period)
  ) %>%
  select(prop, adiagnosekode, period, origin, lpr3) %>%
  as_tsibble(key = c(origin, adiagnosekode), index = period) %>%
  model(arima = ARIMA(prop ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3")

## add the needed x (period) and y (prop) values for plotting
df_mitigation_naive_without_first_quarters_p_values <- df_mitigation_naive_without_first_quarters %>%
  filter(period == max(period)) %>%
  select(period, prop, origin, adiagnosekode) %>%
  left_join(df_mitigation_naive_without_first_quarters_p_values, by = c("origin", "adiagnosekode")) %>%
  mutate(corrected_p <- p.adjust(p.value, "fdr"),
    significant = if_else(corrected_p < 0.05, "*", "")
  )
```



```{r}
source(here("src", "subchapter_props_functions.r"))


graph_subchapter_props(df_mitigation_naive_without_first_quarters,
  filename = "examine_mitigation_without_first_quarters_same_y_axes_with_p_values",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter",
  p_values = df_mitigation_naive_without_first_quarters_p_values,
  nudge_constant = 0.02
)


graph_subchapter_props(df_mitigation_naive_without_first_quarters,
  filename = "examine_mitigation_without_first_quarters_free_y_axes_with_p_values",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter",
  p_values = df_mitigation_naive_without_first_quarters_p_values,
  nudge_frac = 0.02
)
```


<!--chapter:end:subchapter_props/1a_outpatient_naive.rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r}
source(here("rmd", "subchapter_props", "0_setup_env.r"))
```

## Inpatient flow
### Inpatient: Select variables and join LPR2/LPR3 
```{r}
df_inpatient_lpr3 <- df_raw_lpr3 %>%
  filter(pt_type == "Indlagt") %>%
  select(dw_ek_borger, adiagnosekode, datotid_lpr3kontaktstart) %>%
  rename(datotid_start = datotid_lpr3kontaktstart)

df_inpatient_lpr2 <- df_raw_lpr2_inpatient %>%
  select(dw_ek_borger, adiagnosekode, datotid_indlaeggelse) %>%
  rename(datotid_start = datotid_indlaeggelse)

df_inpatient_joined <- bind_rows(df_inpatient_lpr2, df_inpatient_lpr3)

log_time()
```

```{r}
df_inpatient_for_subchapter <- df_inpatient_joined %>%
  keep_only_psych_visits() %>%
  truncate_diagnosis_to_letter_and_digit() %>%
  add_LPR23_quarter_column()

## Examine date parsing
## df_examine <- df_inpatient_for_subchapter %>%
##   filter(datotid_start > ymd("2018-09-01")) %>%
##   filter(datotid_start < ymd("2019-04-01"))

df_unique_in_period_inpatient <- df_inpatient_for_subchapter %>%
  add_column_unique_pt_in_period()

df_unique_with_diagnosis_inpatient <- df_inpatient_for_subchapter %>%
  add_column_n_with_diagnosis_in_period()

df_prop_diag_inpatient <- calc_prop_of_unique_patients_with_diagnosis(
  df_unique_in_period_inpatient,
  df_unique_with_diagnosis_inpatient
)

log_time()
```

```{r}
source(here("src", "subchapter_props_functions.r"))

graph_subchapter_props(df_prop_diag_inpatient,
  filename = "examine_inpatient_same_y_axes",
  date_range = c(ymd("2013-01-01"), ymd("2021-01-01")),
  with_mitigation = FALSE,
  ylabel = "Proportion of inpatients with incident main diagnosis from chapter"
)

graph_subchapter_props(df_prop_diag_inpatient,
  filename = "examine_inpatient_free_y_axes",
  date_range = c(ymd("2013-01-01"), ymd("2021-01-01")),
  with_mitigation = FALSE,
  ylabel = "Proportion of inpatients with incident main diagnosis from chapter"
)

log_time()
```

```{r}
df_prop_diag_inpatient %>%
  mutate(
    lpr3 = if_else(period < "2019-02-03", 0, 1),
    period = yearquarter(period)
  ) %>%
  select(prop, adiagnosekode, period, lpr3) %>%
  as_tsibble(key = adiagnosekode, index = period) %>%
  model(arima = ARIMA(prop ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model)
```

<!--chapter:end:subchapter_props/1b_inpatient.rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r}
source(here("rmd", "subchapter_props", "0_setup_env.r"))
```
# Subchapter props, outpatient constructed
## Run 1a_outpatient_naive.rmd first!
### Construct sequences
```{r}
source(here::here("src", "functions.r"))
df_constructed_outpatient_series <- df_outpatient_for_subchapter %>%
  keep_only_psych_visits() %>%
  construct_sequences(
    clinic_id_col = clinic,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 0,
    verbose = TRUE
  )
```

#### Final visit
```{r}
df_constructed_sequence_final_visit_only <- df_constructed_outpatient_series %>%
  recode_diagnoses_with_last_in_sequence(constructed_id)

df_n_with_diag_in_period_constructed_final_diag <- df_constructed_sequence_final_visit_only %>%
  add_column_n_with_diagnosis_in_period()

df_prop_diag_constructed_sequence_final_visit_only <- calc_prop_of_unique_patients_with_diagnosis(
  df_unique_in_period_outpatient,
  df_n_with_diag_in_period_constructed_final_diag
)
```
#### Most severe visit
```{r}
df_constructed_sequence_most_severe_diag <- df_constructed_outpatient_series %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id)

df_n_with_diag_in_period_constructed_most_severe_diag <- df_constructed_sequence_most_severe_diag %>%
  add_column_n_with_diagnosis_in_period()

df_prop_diag_constructed_sequence_most_severe_diag <- calc_prop_of_unique_patients_with_diagnosis(
  df_unique_in_period_outpatient,
  df_n_with_diag_in_period_constructed_most_severe_diag
)
```

### Plot
```{r}

### Join with the receiver dataframe
df_examine_mitigation_constructed_sequences <- mutate(df_prop_diag_constructed_sequence_most_severe_diag, origin = "Unchanged") %>%
  bind_rows(mutate(df_prop_diag_constructed_sequence_most_severe_diag, origin = "Most severe")) %>%
  bind_rows(mutate(df_prop_diag_constructed_sequence_final_visit_only, origin = "Final visit"))

log_time()
```

```{r}
### Plot
source(here::here("src", "subchapter_props_functions.r"))

graph_subchapter_props(df_examine_mitigation_constructed_sequences,
  filename = "examine_mitigation_constructed_full_same_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

graph_subchapter_props(df_examine_mitigation_constructed_sequences,
  filename = "examine_mitigation_constructed_full_free_y_axes",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter"
)

log_time()
```

### Plot with p-values
```{r}
df_examine_mitigation_constructed_sequences_without_first_quarters <- df_examine_mitigation_constructed_sequences %>%
  filter(period > "2013-01-01")
```

```{r}
pacman::p_load(fable, tsibble, feasts, urca)


df_examine_mitigation_constructed_sequences_without_first_quarters_p_values <- df_examine_mitigation_constructed_sequences_without_first_quarters %>%
  mutate(
    lpr3 = if_else(period < "2019-02-03", 0, 1),
    period = yearquarter(period)
  ) %>%
  select(prop, adiagnosekode, period, origin, lpr3) %>%
  as_tsibble(key = c(origin, adiagnosekode), index = period) %>%
  model(arima = ARIMA(prop ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3")

## add the needed x (period) and y (prop) values for plotting
df_examine_mitigation_constructed_sequences_without_first_quarters_p_values <- df_examine_mitigation_constructed_sequences_without_first_quarters %>%
  filter(period == max(period)) %>%
  select(period, prop, origin, adiagnosekode) %>%
  left_join(df_examine_mitigation_constructed_sequences_without_first_quarters_p_values, by = c("origin", "adiagnosekode")) %>%
  mutate(corrected_p <- p.adjust(p.value, "fdr"),
    significant = if_else(corrected_p < 0.05, "*", "")
  )
```



```{r}
source(here("src", "subchapter_props_functions.r"))


graph_subchapter_props(df_examine_mitigation_constructed_sequences_without_first_quarters,
  filename = "examine_mitigation_constructed_without_first_quarters_full_same_y_axes_with_p_values",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter",
  p_values = df_examine_mitigation_constructed_sequences_without_first_quarters_p_values,
  nudge_constant = 0.02
)


graph_subchapter_props(df_examine_mitigation_constructed_sequences_without_first_quarters,
  filename = "examine_mitigation_constructed_without_first_quarters_full_free_y_axes_with_p_values",
  date_range = c(ymd("2011-06-01"), ymd("2021-01-01")),
  ylabel = "Proportion of outpatients with incident main diagnosis from chapter",
  p_values = df_examine_mitigation_constructed_sequences_without_first_quarters_p_values,
  nudge_frac = 0.02
)
```

<!--chapter:end:subchapter_props/1c_outpatient_constructed_sequences.rmd-->


<!--chapter:end:subchapter_props/index.rmd-->

---
title: "individual_unique_diagnoses_by_date"
output: html_document
editor_options: 
  chunk_output_type: inline
---

# Individual unique diagnoses, inpatient

```{r}
library(here)
source(here("rmd", "individual_unique_diagnoses", "0_setup_env_unique_diagnoses.r"))
```

### Select variables and join LPR2/LPR3 for inpatient
```{r}
df_inpatient_lpr3 <- df_raw_lpr3 %>%
  filter(pt_type == "Indlagt") %>% 
  select(dw_ek_borger, adiagnosekode, datotid_lpr3kontaktstart) %>% 
  rename(datotid_start = datotid_lpr3kontaktstart)

df_inpatient_lpr2 <- df_raw_lpr2_inpatient %>% 
  select(dw_ek_borger, adiagnosekode, datotid_indlaeggelse) %>%
  mutate(dw_sk_forloebsansvar = -1) %>% 
  rename(datotid_start = datotid_indlaeggelse)

df_inpatient_joined <- bind_rows(df_inpatient_lpr2, df_inpatient_lpr3)

log_time()
  
```

```{r}
df_inpatient_for_individual <- df_inpatient_joined %>% 
  add_LPR23_quarter_column() %>% 
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE)
```

<!--chapter:end:individual_unique_diagnoses/1a_inpatient.rmd-->

---
title: "individual_unique_diagnoses_by_date"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
source(here("rmd", "individual_unique_diagnoses", "0_setup_env_unique_diagnoses.r"))
```

# Individual unique diagnoses, outpatient constructed
## Data wrangling 
### Base pre-processing
```{r}
source(here("src", "functions.r"))

df_outpatient_preprocessed <- df_raw_outpatient %>%
  mutate(no_threshold_constructed_id = paste0(dw_ek_borger, shakgeografiafskode_besoeg)) %>%
  keep_only_psych_visits() %>%
  select(
    dw_ek_borger,
    datotid_start,
    adiagnosekode,
    ambbesoeg,
    dw_sk_lpr3forloebsansvar,
    dw_sk_kontakt,
    shakgeografiafskode_besoeg,
    no_threshold_constructed_id
  ) %>%
  add_LPR23_quarter_column() %>%
  filter(period > ymd("2012-05-01"))
```

## No threshold
### Construct sequences
```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_no_threshold <- df_outpatient_preprocessed %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 0,
    verbose = TRUE
  )
```

```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_no_threshold_default <- df_outpatient_constructed_no_threshold %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_no_threshold_most_severe <- df_outpatient_constructed_no_threshold %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_no_threshold_last_visit_only <- df_outpatient_constructed_no_threshold %>%
  recode_diagnoses_with_last_in_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

log_time()
```

### Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "individual_unique_diagnoses_functions.r"))

df_mitigation_constructed_no_threshold_plot <- create_mitigation_df(
  df_default = df_outpatient_constructed_no_threshold_default,
  df_most_severe = df_outpatient_constructed_no_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_no_threshold_last_visit_only
)

mitigation_constructed_no_threshold_plot <- save_mitigation_strategy_plot(df_mitigation_constructed_no_threshold_plot, "mitigation_constructed_no_threshold")

mitigation_constructed_no_threshold_plot
```

## 1m threshold
```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_1m_threshold <- df_outpatient_preprocessed %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 1,
    verbose = TRUE
  )
```

### Construct sequences
```{r}
df_outpatient_constructed_1m_threshold_default <- df_outpatient_constructed_1m_threshold %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_1m_threshold_most_severe <- df_outpatient_constructed_1m_threshold %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_1m_threshold_last_visit_only <- df_outpatient_constructed_1m_threshold %>%
  recode_diagnoses_with_last_in_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)


log_time()
```

### Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "individual_unique_diagnoses_functions.r"))

df_mitigation_constructed_1m_threshold_plot <- create_mitigation_df(
  df_default = df_outpatient_constructed_1m_threshold_default,
  df_most_severe = df_outpatient_constructed_1m_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_1m_threshold_last_visit_only
)

mitigation_constructed_1m_threshold_plot <- save_mitigation_strategy_plot(df_mitigation_constructed_1m_threshold_plot, "mitigation_constructed_1m_threshold")

mitigation_constructed_1m_threshold_plot
```


## 2m threshold
```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_2m_threshold <- df_outpatient_preprocessed %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 2,
    verbose = TRUE
  )
```

### Construct sequences
```{r}
df_outpatient_constructed_2m_threshold_default <- df_outpatient_constructed_2m_threshold %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_2m_threshold_most_severe <- df_outpatient_constructed_2m_threshold %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_2m_threshold_last_visit_only <- df_outpatient_constructed_2m_threshold %>%
  recode_diagnoses_with_last_in_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)


log_time()
```

### Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "individual_unique_diagnoses_functions.r"))

df_mitigation_constructed_2m_threshold_plot <- create_mitigation_df(
  df_default = df_outpatient_constructed_2m_threshold_default,
  df_most_severe = df_outpatient_constructed_2m_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_2m_threshold_last_visit_only
)

mitigation_constructed_2m_threshold_plot <- save_mitigation_strategy_plot(df_mitigation_constructed_2m_threshold_plot, "mitigation_constructed_2m_threshold")

mitigation_constructed_2m_threshold_plot
```


## 3m threshold
```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_3m_threshold <- df_outpatient_preprocessed %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 3,
    verbose = TRUE
  )
```

### Construct sequences
```{r}
df_outpatient_constructed_3m_threshold_default <- df_outpatient_constructed_3m_threshold %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_3m_threshold_most_severe <- df_outpatient_constructed_3m_threshold %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_3m_threshold_last_visit_only <- df_outpatient_constructed_3m_threshold %>%
  recode_diagnoses_with_last_in_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)


log_time()
```

### Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "individual_unique_diagnoses_functions.r"))

df_mitigation_constructed_3m_threshold_plot <- create_mitigation_df(
  df_default = df_outpatient_constructed_3m_threshold_default,
  df_most_severe = df_outpatient_constructed_3m_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_3m_threshold_last_visit_only
)

mitigation_constructed_3m_threshold_plot <- save_mitigation_strategy_plot(df_mitigation_constructed_3m_threshold_plot, "mitigation_constructed_3m_threshold")

mitigation_constructed_3m_threshold_plot
```

## 6m threshold
```{r}
source(here("src", "functions.r"))

df_outpatient_constructed_6m_threshold <- df_outpatient_preprocessed %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 6,
    verbose = TRUE
  )
```

### Construct sequences
```{r}
df_outpatient_constructed_6m_threshold_default <- df_outpatient_constructed_6m_threshold %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_6m_threshold_most_severe <- df_outpatient_constructed_6m_threshold %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)

df_outpatient_constructed_6m_threshold_last_visit_only <- df_outpatient_constructed_6m_threshold %>%
  recode_diagnoses_with_last_in_sequence(constructed_id) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)


log_time()
```

### Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "individual_unique_diagnoses_functions.r"))

df_mitigation_constructed_6m_threshold_plot <- create_mitigation_df(
  df_default = df_outpatient_constructed_6m_threshold_default,
  df_most_severe = df_outpatient_constructed_6m_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_6m_threshold_last_visit_only
)

mitigation_constructed_6m_threshold_plot <- save_mitigation_strategy_plot(df_mitigation_constructed_6m_threshold_plot, "mitigation_constructed_6m_threshold")

mitigation_constructed_6m_threshold_plot
```



## Plots with P-values
### Mitigation, no threshold
```{r}
df_mitigation <- create_mitigation_df(
  df_default = df_outpatient_constructed_no_threshold_default,
  df_most_severe = df_outpatient_constructed_no_threshold_most_severe,
  df_last_visit_only = df_outpatient_constructed_no_threshold_last_visit_only,
  filter_mitigation = FALSE
)

pacman::p_load(fable, tsibble, feasts, urca)

## Binary indicator for date in LPR2/LPR3
df_mitigation <- df_mitigation %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1))
```

```{r}
## What to report?
## pdq(0,0,0) = linear model / t.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing
df_mitigation_p_values <- df_mitigation %>%
  mutate(period = yearquarter(period)) %>%
  select(mean_2, period, origin, lpr3) %>%
  as_tsibble(key = origin, index = period) %>%
  model(arima = ARIMA(mean_2 ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  ungroup() %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr"),
    significant = if_else(corrected_p < 0.05, "*", "")
  )
```

```{r}
df_mitigation_p_values <- df_mitigation %>%
  filter(period == max(period)) %>%
  select(period, mean_2, origin) %>%
  left_join(df_mitigation_p_values, by = "origin")

df_mitigation_p_values
```

```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

p <- save_mitigation_strategy_plot(df_mitigation,
  "mitigation_constructed_p_values",
  p_values = df_mitigation_p_values,
)

p
```

```{r}
ggsave(here::here("figures", "individual_unique_diagnoses_analyses", "constructed_individual_unique_diagnoses_mitigation_with_p_values.png"), 
       plot = p, 
       width = 10,
       height = 5,
       dpi = 600)
```

## Hypothesis-testing
### Truncation
Hypothesis test: was there a change diagnoses during the transition?
```{r}

## binary indicator for date in LPR2/LPR3
df_truncation <- df_truncation %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1))


## What to report?
## pdq(0,0,0) = linear model / t.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing
df_truncation %>%
  mutate(period = yearquarter(period)) %>%
  as_tsibble(key = truncation, index = period) %>%
  model(arima = ARIMA(mean ~ 1 + lpr3 + pdq(1, 1, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model)
```

<!--chapter:end:individual_unique_diagnoses/1b_outpatient_constructed.rmd-->

---
title: "individual_unique_diagnoses_by_date"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
library(here)
source(here("rmd", "individual_unique_diagnoses", "0_setup_env_unique_diagnoses.r"))
```


# Individual unique diagnoses, outpatient naive
## Data wrangling 
Common base
```{r}
df_raw_outpatient_preprocessed <- df_raw_outpatient %>%
  select(
    dw_ek_borger,
    datotid_start,
    adiagnosekode,
    ambbesoeg,
    dw_sk_kontakt,
    dw_sk_lpr3forloebsansvar
  ) %>%
  filter(ambbesoeg == 1) %>%
  keep_only_psych_visits() %>%
  add_LPR23_quarter_column() %>%
  filter(period > ymd("2012-05-01"))
```

### Base dataframes
```{r}
source(here("src", "functions.r"))
df_outpatient_for_individual <- df_raw_outpatient_preprocessed %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = TRUE)
```

```{r}
df_outpatient_most_severe <- df_raw_outpatient_preprocessed %>%
  recode_with_most_severe_diagnosis_for_sequence(dw_sk_kontakt, 
                                                 dw_sk_lpr3forloebsansvar, 
                                                 two_columns = TRUE) %>% 
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)
```

```{r}
df_outpatient_last_visit_only <- df_raw_outpatient_preprocessed %>%
  recode_diagnoses_with_last_in_sequence(dw_sk_kontakt,
    dw_sk_lpr3forloebsansvar,
    two_columns = TRUE
  ) %>%
  gen_unique_diagnoses_pr_patient(confidence_intervals = TRUE, truncation_levels = FALSE)
```

```{r}
log_time()

```

## Truncation
```{r}
df_truncation <- df_outpatient_for_individual %>%
  filter(period > ymd("2012-12-31")) %>%
  pivot_longer(
    cols = c(
      mean_1, mean_2, mean_3, mean_4,
      lcl_1, lcl_2, lcl_3, lcl_4,
      ucl_1, ucl_2, ucl_3, ucl_4
    ),
    names_to = "unit_length"
  ) %>%
  separate(unit_length, into = c("unit", "truncation"), sep = "_") %>%
  pivot_wider(
    names_from = unit,
    values_from = value
  ) %>%
  mutate(truncation = case_when(
    truncation == 1 ~ "FX",
    truncation == 2 ~ "FXX",
    truncation == 3 ~ "FXX.X",
    truncation == 4 ~ "FXX.XX"
  ))
```

## Plotting
```{r fig.height=5, fig.width=10}
log_time()
source(here("src", "ggplot_defaults.r"))
source(here("src", "individual_unique_diagnoses_functions.r"))
```

### Mitigation
```{r}
source(here("src", "functions.r"))

df_mitigation_without_first_quarters <- create_mitigation_df(
  df_default = df_outpatient_for_individual,
  df_most_severe = df_outpatient_most_severe,
  df_last_visit_only = df_outpatient_last_visit_only,
  filter_mitigation = FALSE
)
  
pacman::p_load(fable, tsibble, feasts, urca)


## What to report?
## pdq(0,0,0) = linear model / t.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing
df_mitigation_without_first_quarters_p_values <- df_mitigation_without_first_quarters %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1)) %>% 
  mutate(period = yearquarter(period)) %>%
  select(mean_2, period, origin, lpr3) %>%
  ## pivot_longer(cols=starts_with("mean"), names_to = "mean_n") %>%
  as_tsibble(key = origin, index = period) %>%
  model(arima = ARIMA(mean_2 ~ 1 + lpr3 + pdq(0, 0, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  ungroup() %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr"),
    significant = if_else(corrected_p < 0.05, "*", "")
  )

df_mitigation_without_first_quarters_p_values <- df_mitigation_without_first_quarters %>%
   filter(period == max(period)) %>%
   select(period, mean_2, origin) %>%
   left_join(df_mitigation_without_first_quarters_p_values, by = "origin")
```


```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

p <- save_mitigation_strategy_plot(df_mitigation_without_first_quarters,
  "examine_mitigation_individual_unique_diagnoses_by_quarter_p_values",
  p_values = df_mitigation_without_first_quarters_p_values,
  nudge_constant = 0.001
)

p
```




### Truncation
```{r}

## binary indicator for date in LPR2/LPR3
df_truncation <- df_truncation %>%
  mutate(lpr3 = if_else(period < "2019-02-03", 0, 1))


## What to report?
## pdq(0,0,0) = linear model / t.test (no detrending)
## pdq(0,1,0) = liear model with differencing
## pdq(1,1,0) = autoregressive model with differencing
df_truncation_p_values <- df_truncation %>%
  mutate(period = yearquarter(period)) %>%
  as_tsibble(key = truncation, index = period) %>%
  model(arima = ARIMA(mean ~ 1 + lpr3 + pdq(1, 1, 0) + PDQ(0, 0, 0))) %>%
  coef() %>%
  select(!.model) %>%
  filter(term == "lpr3") %>%
  mutate(
    corrected_p = p.adjust(p.value, "fdr"),
    significant = if_else(corrected_p < 0.05, "*", "")
  )


df_truncation_p_values <- df_truncation %>%
  mutate(period = as.Date(period)) %>%
  filter(period == max(period)) %>%
  select(period, mean, truncation) %>%
  left_join(df_truncation_p_values, by = "truncation")
```

```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))

truncation_plot <- save_truncation_plot(df_truncation,
  "examine_truncation_individual_unique_diagnoses_by_quarter_p_values",
  p_values = df_truncation_p_values
)

truncation_plot
```

### Combined
```{r}
source(here("src", "individual_unique_diagnoses_functions.r"))
log_time()

combined <- save_combined_plots(truncation_plot, p, "combined_naive_individual_unique_diagnoses_with_p_values")

combined
```

<!--chapter:end:individual_unique_diagnoses/1b_outpatient_naive.rmd-->

---
title: "debug_construct_sequences"
output: html_document
editor_options: 
  chunk_output_type: inline
---

## Do we lose visits when using thresholds?

```{r}
df_threshold_summarised <- df_outpatient_constructed_3m_threshold_last_visit_only
df_naive_summarised <- df_outpatient_constructed_no_threshold_last_visit_only

df_source_threshold <- df_outpatient_constructed_3m_threshold
df_source_naive <- df_outpatient_constructed_no_threshold
```


Are there an identical number of patients in periods?
```{r}
identical(
  df_threshold_summarised$n,
  df_naive_summarised$n
)
```

Is the NA rate the same?
```{r}
pacman::p_load(skimr)

skim(df_source_threshold)
skim(df_source_naive)
```

Are the source-DF dimensions the same?
```{r}
dim(df_source_threshold)
dim(df_source_naive)
```

What does "NA introduced by coercion" mean when running `recode_with_most_severe_diagnosis_for_sequence`?

```{r}
source(here("src", "functions.r"))

## undebug(recode_with_most_severe_diagnosis_for_sequence)

df_threshold_most_severe <- df_source_threshold %>%
  slice_sample(prop = 0.01) %>%
  mutate(adiagnosekode_2 = substr(adiagnosekode, 2, 2)) %>%
  recode_with_most_severe_diagnosis_for_sequence(constructed_id)

df_threshold_most_severe %>%
  filter(adiagnosekode_2 == "e")
```

For some reason, about 10% of the rows don't have psychiatric diagnosis codes. This should be fixed now, since I added "keep_only_psych_visits" to preprocessing

<!--chapter:end:individual_unique_diagnoses/1c_debug_construct_diagnoses.Rmd-->


<!--chapter:end:individual_unique_diagnoses/index.rmd-->


<!--chapter:end:stability_connected_series/index.rmd-->

---
editor_options:
  chunk_output_type: inline
output:
  html_document: default
always_allow_html: yes
---
# Stability connected series, constructed

```{r}
pacman::p_load(DBI, data.table, dtply, dplyr, lubridate, ggplot2, stringr, tidyr, ggalluvial, here)

source("E:/Users/adminmanber/Desktop/FeasibilityMapper/utils.r")
source(here("src", "functions.r"))
```

## General data wrangling
```{r get-raw}
df_raw <- get_fct("FOR_besoeg_fysiske_fremmoeder") %>%
  clean_sql_import()
```

## No threshold
### Data wrangling
```{r construct-no-threshold}
df_constructed_no_threshold <- df_raw %>%
  keep_only_psych_visits() %>%
  mutate(adiagnosekode = substring(adiagnosekode, 1, 2)) %>%
  construct_sequences(
    clinic_id_col = shakgeografiafskode_besoeg,
    patient_id_col = dw_ek_borger,
    date_col = datotid_start,
    threshold_months = 0,
    verbose = TRUE
  )

log_time()
```

```{r}
df_with_contact_counts_constructed_no_threshold <- df_constructed_no_threshold %>%
  group_by(constructed_id) %>%
  arrange(datotid_start, .by_group = T) %>%
  mutate(contact_nr = row_number()) %>%
  group_by(constructed_id) %>%
  mutate(total_contacts = max(contact_nr))

log_time()
```

### Plotting
```{r}
## Changes over n_visits
df_one_row_per_sequence_constructed_no_threshold <- df_with_contact_counts_constructed_no_threshold %>%
  ## filter(total_contacts > 1) %>% ## Want to also visualise contacts that aren't part of a connected series
  group_by(constructed_id) %>%
  mutate(first_diagnosis = str_c(adiagnosekode)) %>%
  mutate(last_diagnosis = str_c(last(adiagnosekode))) %>%
  filter(contact_nr == 1)

log_time()
```


```{r}
df_alluvial_final_constructed_no_threshold <- df_one_row_per_sequence_constructed_no_threshold %>%
  filter(substr(first_diagnosis, 1, 1) == "Z" | substr(first_diagnosis, 1, 1) == "F") %>%
  mutate(first_diagnosis = ifelse(substr(first_diagnosis, 1, 1) == "Z", "ZX", first_diagnosis)) %>%
  mutate(last_diagnosis = ifelse(substr(last_diagnosis, 1, 1) == "Z", "ZX", last_diagnosis)) %>%
  mutate(diagnosis_changed = ifelse(first_diagnosis == last_diagnosis, 0, 1)) %>%
  filter(substr(last_diagnosis, 1, 1) == "Z" | substr(last_diagnosis, 1, 1) == "F") %>%
  filter(first_diagnosis != "ZX") %>%
  filter(last_diagnosis != "ZX")

log_time()
```

```{r}
allu_df_summarized_constructed_no_threshold <- df_alluvial_final_constructed_no_threshold %>%
  group_by(first_diagnosis, last_diagnosis) %>%
  summarize(n = n()) %>%
  filter(n > 5)

log_time()
```

```{r}
source(here("src", "stability_connected_series_functions.r"))

save_alluvial_plot(
  df = allu_df_summarized_constructed_no_threshold,
  filename = "allu_first_last_constructed_no_threshold"
)

log_time()
```

```{r}
first_diagnosis_table <- gen_first_diagnosis_table(df_alluvial_final_constructed_no_threshold)

last_diagnosis_table <- gen_last_diagnosis_table(df_alluvial_final_constructed_no_threshold)
```

### Tables
```{r}
library("kableExtra")

first_diagnosis_table %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```
```{r}
library("kableExtra")

last_diagnosis_table %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

<!--chapter:end:stability_connected_series/stability_connected_series_constructed.Rmd-->

---
editor_options:
  chunk_output_type: inline
output:
  html_document: default
always_allow_html: yes
---
# Stability connected series, naive

```{r}
pacman::p_load(DBI, data.table, dtply, dplyr, lubridate, ggplot2, stringr, tidyr, ggalluvial, here)

source("E:/Users/adminmanber/Desktop/FeasibilityMapper/utils.r")
source(here("src", "functions.r"))
```

##################
## Data wrangling #
##################
```{r}
df_raw <- get_fct("FOR_besoeg_fysiske_fremmoeder") %>%
  clean_sql_import()

df <- df_raw %>%
  keep_only_psych_visits() %>%
  select(
    "dw_ek_borger",
    "datotid_start",
    "dw_sk_lpr3forloebsansvar",
    "adiagnosekode"
  ) %>%
  mutate(adiagnosekode = substring(adiagnosekode, 1, 2))

log_time()
```

```{r}
df_with_contact_counts <- df %>%
  group_by(dw_sk_lpr3forloebsansvar) %>%
  arrange(datotid_start, .by_group = T) %>%
  mutate(contact_nr = row_number()) %>%
  group_by(dw_sk_lpr3forloebsansvar) %>%
  mutate(total_contacts = max(contact_nr))

log_time()
```

######################
### Alluvial diagram ##
######################

```{r}
## Changes over n_visits
df_one_row_per_connected_series <- df_with_contact_counts %>%
  ## filter(total_contacts > 1) %>% ## Want to also visualise contacts that aren't part of a connected series
  group_by(dw_sk_lpr3forloebsansvar) %>%
  mutate(first_diagnosis = str_c(adiagnosekode)) %>%
  mutate(last_diagnosis = str_c(last(adiagnosekode))) %>%
  filter(contact_nr == 1)

log_time()
```


```{r}
df_alluvial_final <- df_one_row_per_connected_series %>%
  filter(substr(first_diagnosis, 1, 1) == "Z" | substr(first_diagnosis, 1, 1) == "F") %>%
  mutate(first_diagnosis = ifelse(substr(first_diagnosis, 1, 1) == "Z", "ZX", first_diagnosis)) %>%
  mutate(last_diagnosis = ifelse(substr(last_diagnosis, 1, 1) == "Z", "ZX", last_diagnosis)) %>%
  mutate(diagnosis_changed = ifelse(first_diagnosis == last_diagnosis, 0, 1)) %>%
  filter(substr(last_diagnosis, 1, 1) == "Z" | substr(last_diagnosis, 1, 1) == "F") %>%
  filter(first_diagnosis != "ZX") %>%
  filter(last_diagnosis != "ZX")

log_time()
```

```{r}
allu_df_summarized <- df_alluvial_final %>%
  group_by(first_diagnosis, last_diagnosis) %>%
  summarize(n = n()) %>%
  filter(n > 5)

log_time()
```

```{r}
source(here("src", "stability_connected_series_functions.r"))

save_alluvial_plot(df = allu_df_summarized, 
                   filename = "allu_first_last_naive")

log_time()
```

```{r}
first_diagnosis_table <- gen_first_diagnosis_table(df_alluvial_final)
write.csv(first_diagnosis_table, here("tables", "first_diagnosis.csv"))

last_diagnosis_table <- gen_last_diagnosis_table(df_alluvial_final)
write.csv(last_diagnosis_table, here("tables", "last_diagnosis.csv"))
```

```{r}
library("kableExtra")

first_diagnosis_table %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```
```{r}
library("kableExtra")

last_diagnosis_table %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

<!--chapter:end:stability_connected_series/stability_connected_series_naive.Rmd-->

